Delay Comparison of Different Switch Architectures

### 2013-11-14 MSReport/MSThesis.tex
wrote some conclusions and am trying out the admission control for tcp need to verify with jean why that is warranted.

\section{Open Loop Simulations}

@@

\section{Closed Loop (TCP) Simulations}
\begin{figure}%[h]
	% \includegraphics[width=90mm]{typical_flows.png}
	\caption{This graph represents the flow matrix of a `typical' datacenter load.  Where $80\%$ of the flows (type 2) generate a low volume of traffic and are sensitive to delays.  The other $20\%$ of flows (type 1) generate a large volume of traffic and are require a high throughput but not necessarily low delays.  The color in the $s,d$th position signifies the type of flow going from input $s$ to output $d$.  Flows of type $0$ do not generate any packets.} 	
	\label{typical_flows}
\end{figure}

@@

@@

Notice that there is no effort to save the events that merge discards.  This is because the stochastic events are generated in a memoryless fashion parametrized by the state (i.e. either occur or do not with the same probability at each time step).  The deterministic events are all a function of the state and can be recalculated from the new state that results after the application of an earlier event.  The ACKs are stored in the event$\_$heap, but could in theory also have their own state variable.  Other deterministic events could also be stored in the event$\_$heap if the depending on the preference of the coder.

\subsection{Auxiliary structures}

>>>>

\section{Open Loop Simulations} \label{open}

@@

\section{Closed Loop (TCP) Simulations} \label{closed}
\begin{figure}%[h]
	% \includegraphics[width=90mm]{typical_flows.png}
	\caption{This graph represents the flow matrix of a `typical' datacenter load.  Where $80\%$ of the flows (type 2) generate a low volume of traffic and are sensitive to delays.  The other $20\%$ of flows (type 1) generate a large volume of traffic and are require a high throughput but not necessarily low delays.  The color in the $s,d$th position signifies the type of flow going from input $s$ to output $d$.  Flows of type $0$ do not generate any packets.} 	
	\label{typical_flows}
\end{figure}

@@

\section{Conclusions}

Our open loop experiments (\S\ref{open}) confirmed the intuition that there is something to be gained from using the provably optimal QCSMA scheduling algorithm over iterative SLIP, although this effect only exhibits itself under high loads.  The open loop simulations also underscored the need for bookkeeping the length of the packets, as opposed to simulating a simpler scenario with equal length packets.  This is because the QCSMA algorithm works best when fewer inputs are competing for the available outputs, which is aided by a large variation in packets lengths.

In contrast, the closed loop simulations (\S \ref{closed}) we considered suggest that although there is a differentiation of performance between QCSMA and SLIP, it seems to play a negligible roll in practice.  This is partly because the congestion levels (i.e. the loads) are adequately regulated using TCP or a similar congestion control mechanism, and partly because of the low level of intercommunication loads observed in real datacenters.  Perhaps as the prevalence of cloud based distributed application increases, this may change.

@@

Notice that there is no effort to save the events that merge discards.  This is because the stochastic events are generated in a memoryless fashion parametrized by the state (i.e. either occur or do not with the same probability at each time step).  The deterministic events are all a function of the state and can be recalculated from the new state that results after the application of an earlier event.  The ACKs are stored in the event$\_$heap, but could in theory also have their own state variable.  Other deterministic events could also be stored in the event$\_$heap depending on the preference of the coder.

\begin{itemize}
\item To illustrate what the functions called by next$\_$event() look like we have the example of:
\item To add a component to the simulator, need to modify:
\item switch statements 
\end{itemize}
\subsection{Auxiliary structures}
\begin{itemize}
\item variable collections and switch statements
\item Data Collector Class
\item Matlab
\item log
\end{itemize}
